---
title: "Descriptives"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Loading final data set from Targets cache

```{r loading data}
targets::tar_load("final_data")
d <- final_data
rm(final_data)
```

## Variables used in the analysis

### Tweet level

* status_id
* user_id
* created_at
* dl_at: time of download of tweet in UTC time
* text: text as returned by the Twitter API
* text_clean: text without links, tags, line breaks, punctuation, "&amp" encoding and redundant white space
* is_retweet
* is_quote
* favorite_count
* retweet_count
* lang: only languages that were recognized as English by Twitter's AI were included in final data set
* nchar: number of character of text_clean
* nwords: number of word of text_clean

### User level

* is_teacher: 1 if user was classified as teacher by our ML model by his bio at time of download (dl_at) with ambiguous classifications over time randomized and standardized across measurement points
* description: user's bio on which teacher classification was based on (with the exception of changing bios over time that elicited both classifications as teacher and as non-teacher which where later randomized)

### Context variables

* isChat: 1 if tweet was posted inside of #NGSSchat chat session, 0 if not, NA if tweet does not include #NGSSchat
* q: variable with the levels "#NGSSchat", "ngss" and "other" representing if the tweet includes #NGSSchat, the term ngss (and not #NGSSchat) or any other NGSS-related search term (and not the two aformentioned terms)

### Sentiment variables (by class; featuring SentiStrength, LIWC, Tidytext)

* {method}_pos: Positivity rating of tweet. Standardized by number of words for Tidytext rating and truncated to 4 for SentiStrength rating.
* {method}_neg: Negativity rating of tweet. Standardized by number of words for Tidytext rating and truncated to 4 for SentiStrength rating.
* {method}_scale: Positivity + Negativity rating (if negativity score is { 0, else minus)
* {method}_{pos/neg/scale}_scaled: base::scale() applied to individiual ratings
* {method}_binary: Binary (pos/neg) rating of tweets by method for validation. SentiStrength's binary method was employed and for LIWC and Tidytext, a positive classification was assigned if the respective scale was }= 0.

* {method}_ambi: Ambiguity control measure defined as the sum of the absolute differences from 0 for each method's positivity and negativity ratings

* {method}_{method}_discrepancy_{pos/neg/scale}: Squared difference between base::scaled() ratings (positivity, negativity, scale) for all three pairs of methods. NaN if no comparison was possible due to NAs
* total_discrepancy_{pos/neg/scale}: Sum of pair-wise discrepancies for all three ratings (positivity, negativity, scale), dividied by the number of available comparisons.
* n_combinations_{pos/neg/scale}: Number of available comparisons for total_discrepancy_{pos/neg/scale} for later reference. Currently this index is equally large for pos/neg/scale alike, as 0s were assigned in tidytext dictionary approaches when at least one match (positive or negative) was found. CB: We might want to re-discuss this, it seems to alter results quite a bit.

## Sample and a glimspe at the variables

```{r sample}
d$is_teacher <- as.factor(d$is_teacher)
d$ss_binary <- as.factor(d$ss_binary)
d$liwc_binary <- as.factor(d$liwc_binary)
d$tidytext_binary <- as.factor(d$tidytext_binary)
d$n_combinations_scale <- as.factor(d$n_combinations_scale)
d %>% 
  select(status_id, user_id,
         created_at, dl_at,
         favorite_count, retweet_count,
         nchar, nwords,
         is_teacher, isChat, q,
         ss_binary, liwc_binary, tidytext_binary,
         ss_pos_scaled, ss_neg_scaled, ss_scale_scaled,
         liwc_pos_scaled, liwc_neg_scaled, liwc_scale_scaled,
         tidytext_pos_scaled, tidytext_neg_scaled, tidytext_scale_scaled,
         ss_ambi, liwc_ambi, tidytext_ambi,
         total_discrepancy_pos, total_discrepancy_neg, total_discrepancy_scale,
         n_combinations_scale
         ) %>% 
  skimr::skim()
```

## Correlations pos scales

```{r correlations scales pos}
d %>% 
  select(
         ss_pos_scaled, liwc_pos_scaled, tidytext_pos_scaled
         ) %>% 
  select_if(is.numeric) %>% 
  corrr::correlate() %>% 
  corrr::fashion() %>%
  knitr::kable()
```

## Correlations neg scales

```{r correlations scales neg}
d %>% 
  select(
         ss_neg_scaled, liwc_neg_scaled, tidytext_neg_scaled
         ) %>% 
  select_if(is.numeric) %>% 
  corrr::correlate() %>% 
  corrr::fashion() %>%
  knitr::kable()
```

## Correlations overall scales

```{r correlations scales overall}
d %>% 
  select(
         ss_scale_scaled, liwc_scale_scaled, tidytext_scale_scaled
         ) %>% 
  select_if(is.numeric) %>% 
  corrr::correlate() %>% 
  corrr::fashion() %>%
  knitr::kable()
```

## Confusion matrix Sentistrength, LIWC

```{r confusion matrix Sentistrength LIWC}
d$ss_binary <- factor(d$ss_binary, levels=c(-1, 1), labels=c(0, 1))
d$liwc_binary <- as.factor(d$liwc_binary)
print("PREDICTION: Sentistrength; REFERENCE: LIWC")
caret::confusionMatrix(data=d$ss_binary, reference=d$liwc_binary)
```

## Confusion matrix LIWC, Tidytext - Excluding Tidytext non-matches

```{r confusion matrix LIWC Tidytext}
d$tidytext_binary <- as.factor(d$tidytext_binary)
d$liwc_binary <- as.factor(d$liwc_binary)
print("PREDICTION: Tidytext; REFERENCE: LIWC")
caret::confusionMatrix(data=d$tidytext_binary, reference=d$liwc_binary)
```

## Confusion matrix Sentistrength, Tidytext - Excluding Tidytext non-matches

```{r confusion matrix Sentistrength Tidytext}
d$ss_binary[d$ss_binary == -1] <- 0
d$ss_binary <- as.factor(d$ss_binary)
d$tidytext_binary <- as.factor(d$tidytext_binary)
print("PREDICTION: Sentistrength; REFERENCE: Tidytext")
caret::confusionMatrix(data=d$ss_binary, reference=d$tidytext_binary)
```

## Correlations ambiguity measures

```{r correlations ambiguity measures}
d %>% 
  select(
         ss_ambi, liwc_ambi, tidytext_ambi
         ) %>% 
  select_if(is.numeric) %>% 
  corrr::correlate() %>% 
  corrr::fashion() %>%
  knitr::kable()
```

## Individual tidytext dictionary coverage

```{r dictionary coverage, echo=FALSE}
  print("descriptives_coverage")
  print("bing")
  print((d$bing_scale %>% is.na() %>% `!` %>% sum() * 100 / nrow(d)) %>% round(2))
  print("afinn")
  print((d$afinn_scale %>% is.na() %>% `!` %>% sum() * 100 / nrow(d)) %>% round(2))
  print("loughran")
  print((d$loughran_scale %>% is.na() %>% `!` %>% sum() * 100 / nrow(d)) %>% round(2))
  print("nrc")
  print((d$nrc_scale %>% is.na() %>% `!` %>% sum() * 100 / nrow(d)) %>% round(2))
  print("tidytext_scale")
  print((d$tidytext_scale %>% is.na() %>% `!` %>% sum() * 100 / nrow(d)) %>% round(2)) 
```

## Pair-wise discrepancies

```{r pair-wise discrepancies pos}
d %>% select(
  "ss_liwc_discrepancy_pos",
  "ss_tidytext_discrepancy_pos",
  "liwc_tidytext_discrepancy_pos",
  "ss_liwc_discrepancy_neg",
  "ss_tidytext_discrepancy_neg",
  "liwc_tidytext_discrepancy_neg",
  "ss_liwc_discrepancy_scale",
  "ss_tidytext_discrepancy_scale",
  "liwc_tidytext_discrepancy_scale",
  "total_discrepancy_pos",
  "total_discrepancy_neg",
  "total_discrepancy_scale"
  ) %>%
  colMeans(na.rm=T) %>%
  knitr::kable(digits = 2, col.names = "mean")
```

## Discrepancy by context

```{r discrepancy by context}
d %>% select(
  "total_discrepancy_pos",
  "total_discrepancy_neg",
  "total_discrepancy_scale",
  "q",
  ) %>% 
  group_by(q) %>%
  summarise_all(mean) %>%
  knitr::kable(digits = 2)
```

## Discrepancy by teacher, non-teacher

```{r discrepancy by teacher non-teacher}
d %>% select(
  "total_discrepancy_pos",
  "total_discrepancy_neg",
  "total_discrepancy_scale",
  "is_teacher",
  ) %>% 
  group_by(is_teacher) %>%
  summarise_all(mean) %>%
  knitr::kable(digits = 2)
```

## Discrepancy by isChat

```{r discrepancy by isChat}
d %>% select(
  "total_discrepancy_pos",
  "total_discrepancy_neg",
  "total_discrepancy_scale",
  "isChat",
  ) %>% 
  group_by(isChat) %>%
  summarise_all(mean) %>%
  knitr::kable(digits = 2)
```

## Sentiment Ratio (SentiStrenght, as in AERA open paper) by context

```{r}
d %>% select(
  "ss_binary",
  "q"
  ) %>% 
  group_by(q, ss_binary) %>%
  count() %>%
  ungroup() %>%
  spread(ss_binary, n) %>%
  mutate(Sentiment_Ratio = `1`/`0`) %>%
  knitr::kable(digits = 2)
```

## Sentiment Ratio (SentiStrenght, as in AERA open paper) by teacher, non-teacher

```{r}
d %>% select(
  "ss_binary",
  "is_teacher"
  ) %>% 
  group_by(is_teacher, ss_binary) %>%
  count() %>%
  ungroup() %>%
  spread(ss_binary, n) %>%
  mutate(Sentiment_Ratio = `1`/`0`) %>%
  knitr::kable(digits = 2)
```

## Sentiment Ratio (SentiStrenght, as in AERA open paper) by by isChat

```{r}
d %>% select(
  "ss_binary",
  "isChat"
  ) %>% 
  group_by(isChat, ss_binary) %>%
  count() %>%
  ungroup() %>%
  spread(ss_binary, n) %>%
  mutate(Sentiment_Ratio = `1`/`0`) %>%
  knitr::kable(digits = 2)
```

## Ambiguity by context

```{r ambiguity by context}
d %>% select(
  "ss_ambi",
  "liwc_ambi",
  "tidytext_ambi",
  "q",
  ) %>% 
  group_by(q) %>%
  summarise_all(mean, na.rm=T) %>%
  knitr::kable(digits = 2)
```

## Ambiguity by teacher, non-teacher

```{r ambiguity by teacher non-teacher}
d %>% select(
  "ss_ambi",
  "liwc_ambi",
  "tidytext_ambi",
  "is_teacher",
  ) %>% 
  group_by(is_teacher) %>%
  summarise_all(mean, na.rm=T) %>%
  knitr::kable(digits = 2)
```

## Ambiguity by isChat

```{r ambiguity by isChat}
d %>% select(
  "ss_ambi",
  "liwc_ambi",
  "tidytext_ambi",
  "isChat",
  ) %>% 
  group_by(isChat) %>%
  summarise_all(mean, na.rm=T) %>%
  knitr::kable(digits = 2)
```

## Correlations discrepancy 

```{r correlations discrepancy}
d %>% 
  select(nchar, nwords,
         favorite_count, retweet_count,
         ss_ambi, liwc_ambi, tidytext_ambi, 
         total_discrepancy_pos, total_discrepancy_neg, total_discrepancy_scale
         ) %>% 
  select_if(is.numeric) %>% 
  corrr::correlate() %>% 
  select(rowname, total_discrepancy_pos, total_discrepancy_neg, total_discrepancy_scale) %>%
  corrr::fashion() %>%
  knitr::kable()
```

```{r correlations discrepancy sqrt transformed}
d$total_discrepancy_pos_sqrt <- d$total_discrepancy_pos %>% sqrt
d$total_discrepancy_neg_sqrt <- d$total_discrepancy_neg %>% sqrt
d$total_discrepancy_scale_sqrt <- d$total_discrepancy_scale %>% sqrt

d %>% 
  select(nchar, nwords,
         favorite_count, retweet_count,
         ss_ambi, liwc_ambi, tidytext_ambi, 
         total_discrepancy_pos_sqrt, total_discrepancy_neg_sqrt, total_discrepancy_scale_sqrt
         ) %>% 
  select_if(is.numeric) %>% 
  corrr::correlate() %>% 
  select(rowname, total_discrepancy_pos_sqrt, total_discrepancy_neg_sqrt, total_discrepancy_scale_sqrt) %>%
  corrr::fashion() %>%
  knitr::kable(caption = "Correlates of dicrepancy measures, sqrt-transformed")
```

```{r correlations discrepancy log transformed}
d$total_discrepancy_pos_log <- d$total_discrepancy_pos %>% log
d$total_discrepancy_neg_log <- d$total_discrepancy_neg %>% log
d$total_discrepancy_scale_log <- d$total_discrepancy_scale %>% log

d %>% 
  select(nchar, nwords,
         favorite_count, retweet_count,
         ss_ambi, liwc_ambi, tidytext_ambi, 
         total_discrepancy_pos_log, total_discrepancy_neg_log, total_discrepancy_scale_log
         ) %>% 
  select_if(is.numeric) %>% 
  corrr::correlate() %>% 
  select(rowname, total_discrepancy_pos_log, total_discrepancy_neg_log, total_discrepancy_scale_log) %>%
  corrr::fashion() %>%
  knitr::kable(caption = "Correlates of dicrepancy measures, log-transformed")
```

## Distribution properties

## Pos

### SentiStrength

```{r}
d %>% 
  ggplot(aes(x = ss_pos)) +
  geom_histogram()
```

### LIWC, many tweets assigned 0 for pos

```{r}
d %>% 
  ggplot(aes(x = liwc_pos)) +
  geom_histogram(bins=100)
```

### Tidytext

```{r}
d %>% 
  ggplot(aes(x = tidytext_pos)) +
  geom_histogram(bins=100)
```

## Neg

### SentiStrength

```{r}
d %>% 
  ggplot(aes(x = ss_neg)) +
  geom_histogram()
```

### LIWC

### Many tweets assigned 0 for neg
```{r}
d %>% 
  ggplot(aes(x = liwc_neg)) +
  geom_histogram()
```

### Without 0s

```{r}
d %>% 
  ggplot(aes(x = liwc_neg)) +
  geom_histogram(bins=150) +
  ylim(0, 15000) + 
  xlim(0, 15)
```

### Tidytext, simlar story, many 0s for neg

```{r}
d %>% 
  ggplot(aes(x = tidytext_neg)) +
  geom_histogram(bins=150)
```

## Ambiguity

### Tidytext

```{r}
d %>% 
  ggplot(aes(x = tidytext_ambi)) +
  geom_histogram(bins=150) +
  xlim(0, 0.5) + 
  ylim(0, 50000)
```
```
### SentiStrength

```{r}
d %>% 
  ggplot(aes(x = ss_ambi)) +
  geom_histogram()
```

### LIWC

```{r}
d %>% 
  ggplot(aes(x = liwc_ambi)) +
  geom_histogram(bins=150) +
  ylim(0, 50000) +
  xlim(0, 40)
```

## Scale, holds many 0 and slightly positive tweets

### SentiStrength

```{r}
d %>% 
  ggplot(aes(x = ss_scale)) +
  geom_histogram()
```

### LIWC

```{r}
d %>% 
  ggplot(aes(x = liwc_scale)) +
  geom_histogram(bins=30)
```

### Tidytext

```{r}
d %>% 
  ggplot(aes(x = tidytext_scale)) +
  geom_histogram(bins=100)
```

## Discrepancy

### Overall, right skwwed but quite normally distributed

```{r}
d %>% 
  ggplot(aes(x = total_discrepancy_scale)) +
  geom_histogram(bins=300)
```

### Pos, right skwwed but quite normally distributed

```{r}
d %>% 
  ggplot(aes(x = total_discrepancy_pos)) +
  geom_histogram(bins=300)
```

### Neg, very right skewed and not normally distributed due to many 0 assignments for negativity

```{r}
d %>% 
  ggplot(aes(x = total_discrepancy_neg)) +
  geom_histogram(bins=100)
```


