---
title: "Descriptives"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading final data set from Targets cache

```{r loading data}
targets::tar_load("final_data")
d <- final_data
rm(final_data)
```

## Variables used in the analysis

### Tweet level

* status_id
* user_id
* created_at
* dl_at: time of download of tweet in UTC time
* text: text as returned by the Twitter API
* text_clean: text without links, tags, line breaks, punctuation, "&amp" encoding and redundant white space
* is_retweet
* is_quote
* favorite_count
* retweet_count
* quote_count
* reply_count
* lang: only languages that were recognized as English by Twitter's AI were included in final data set
* nchar: number of character of text_clean
* nwords: number of word of text_clean

### User level

* followers_count: number of followers of user at time of download (dl_at)
* friends_count: number of followed users of user at time of download (dl_at)
* listed_count: number of affiliated lists of user at time of download (dl_at)
* is_teacher: 1 if user was classified as teacher by our ML model by his bio at time of download (dl_at) with ambiguous classifications over time randomized and standardized across measurement points

### Context variables

* isChat: 1 if tweet was posted inside of #NGSSchat chat session, 0 if not, NA if tweet does not include #NGSSchat
* q: variable with the levels "#NGSSchat", "ngss" and "other" representing if the tweet includes #NGSSchat, the term ngss (and not #NGSSchat) or any other NGSS-related search term (and not the two aformentioned terms)

### Sentiment variables (by class; featuring SentiStrength, LIWC, Tidytext)

* {method}_pos: Positivity rating of tweet. Standardized by number of words for Tidytext rating and truncated to 4 for SentiStrength rating.
* {method}_neg: Negativity rating of tweet. Standardized by number of words for Tidytext rating and truncated to 4 for SentiStrength rating.
* {method}_scale: Positivity + Negativity rating (if negativity score is { 0, else minus)
* {method}_{pos/neg/scale}_scaled: base::scale() applied to individiual ratings
* {method}_binary: Binary (pos/neg) rating of tweets by method for validation. SentiStrength's binary method was employed and for LIWC and Tidytext, a positive classification was assigned if the respective scale was }= 0.

* {method}_ambi: Ambiguity control measure defined as the sum of the absolute differences from 0 for each method's positivity and negativity ratings

* {method}_{method}_discrepancy_{pos/neg/scale}: Squared difference between base::scaled() ratings (positivity, negativity, scale) for all three pairs of methods. NaN if no comparison was possible due to NAs
* total_discrepancy_{pos/neg/scale}: Sum of pair-wise discrepancies for all three ratings (positivity, negativity, scale), dividied by the number of available comparisons.
* n_combinations_{pos/neg/scale}: Number of available comparisons for total_discrepancy_{pos/neg/scale} for later reference




```{r pressure, echo=FALSE}
#plot(pressure)
```


